Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking

### 2021-04-19 博士/论文提交/adversarial_attack/TCSVT/latex/bare_jrnl.tex
扩至9.5页
10页完成

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{images/1_v8.pdf}
  \caption{An illustration of our attacks to SiamFC++ on some example tracking sequences from GOT-10k benchmark. Our approach generates the video-agnostic perturbations which can force SiamFC++ to follow a complicated trajectory at virtually no cost. This is realized by off-line training the perturbations so that the tracker mistakenly believes the \textit{fake target} area contains the object to be tracked (see the left heatmap). Moreover, the quality assessment branch in SiamFC++ is also misled to confirm this result (see the right heatmap). The \textit{fake target} size is gradually decreased.} 
  %Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations. 
  %Red represents the ground-truth bounding box, and green represents the predicted bounding box by the tracker.
  %The purple dashed box marks the universal adversarial patch. The left heatmap represents the probability of each spatial position to contain the \textit{fake target}, and the right heatmap represents the target state estimation quality.}
  \label{fig:1}
\end{figure*}

@@

@@

@@

@@

Translated with www.DeepL.com/Translator (free version)

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images/UAP.png}
  \caption{Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.} 
  \label{fig:UAP}
\end{figure}

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.85\textwidth]{images/1_v8.pdf}
  \caption{An illustration of our attacks to SiamFC++ on some example tracking sequences from GOT-10k benchmark. Our approach generates the video-agnostic perturbations which can force SiamFC++ to follow a complicated trajectory at virtually no cost. This is realized by off-line training the perturbations so that the tracker mistakenly believes the \textit{fake target} area contains the object to be tracked (see the left heatmap). Moreover, the quality assessment branch in SiamFC++ is also misled to confirm this result (see the right heatmap). The \textit{fake target} size is gradually decreased.} 
  %Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations. 
  %Red represents the ground-truth bounding box, and green represents the predicted bounding box by the tracker.
  %The purple dashed box marks the universal adversarial patch. The left heatmap represents the probability of each spatial position to contain the \textit{fake target}, and the right heatmap represents the target state estimation quality.}
  \label{fig:1}
\end{figure*}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{images/state-of-art.png}
  \end{center}
  \caption{fdsafs}
  \label{fig:state-of-art}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{images/iter.png}
  \caption{23} 
  \label{fig:1}
\end{figure*}

@@

We further analyze the perfor-mance of our method with respect to 11 attributes in OTB-2015 [22]. As suggested in OTB [22], the attributes consistof out-of-view (OV), occlusion (OCC), illumination varia-tion (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM),background clutters (BC), motion blur (MB), and in-planerotation (IPR).

@@
